---
title: "STOR 565 Spring 2018 Homework 2"
author: "YOUR NAME"
output:
  pdf_document: default
  html_document: default
subtitle: \textbf{Due on 01/31/2018 in Class}
header-includes: \usepackage{amsgen,amsmath,amstext,amsbsy,amsopn,amssymb,mathabx,amsthm,bm,bbm}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## install.packages("ISLR")   # if you don't have this package, run it
library("ISLR")
library(MASS)
```
\theoremstyle{definition}
\newtheorem*{hint}{Hint}

\theoremstyle{remark}
\newtheorem*{rmk}{Remark}

*Remark.* This homework aims to help you go through the necessary preliminary from linear regression. Credits for **Theoretical Part** and **Computational Part** are in total 100 pt. For **Computational Part**, please complete your answer in the **RMarkdown** file and summit your printed PDF homework created by it.

## Computational Part

1. (*35 pt*) Consider the dataset "Boston" in predicting the crime rate at Boston with associated covariates.
```{r Boston}
head(Boston)
```
Suppose you would like to predict the crime rate with explantory variables

* `medv`  - Median value of owner-occupied homes
* `dis`   - Weighted mean of distances to employement centers
* `indus` - Proportion of non-retail business acres

Run with the linear model
```{r lm}
mod1 <- lm(crim ~ medv + dis + indus, data = Boston)
summary(mod1)
```
Answer the following questions.

(i) What do the following quantities that appear in the above output mean in the linear model? Provide a breif description.
    + `t value` and `Pr(>|t|)` of `medv`
    
    **Answer:** YOUR ANSWER.

    ***
    + `Multiple R-squared`
    
    **Answer:** YOUR ANSWER.
    
    ***
    + `F-statistic`, `DF` and corresponding `p-value`

    **Answer:** YOUR ANSWER.
    
    ***
    

(ii) Are the following sentences True of False? Briefly justify your answer.
    + `indus` is not a significant predictor of crim, and we can drop this from the model.
    
    **Answer:** YOUR ANSWER.
    
    ***
    + `Multiple R-squared` is preferred to `Adjusted R-squared` as it takes into account all the variables.
    
    **Answer:** YOUR ANSWER.

    ***    
    + `medv` has a negative effect on the response.
    
    **Answer:** YOUR ANSWER.
    
    ***
    + Our model residuals appear to be normally distributed.
    
    \begin{hint}
      You need to access to the model residuals in justifying the last sentence. The following commands might help.
    \end{hint}
    ```{r, eval=FALSE}
    # Obtain the residuals
    res1 <- residuals(mod1)
    
    # Normal QQ-plot of residuals
    plot(mod1, 2)
    
    # Conduct a Normality test via Shapiro-Wilk and Kolmogorov-Smirnov test
    shapiro.test(res1)
    ks.test(res1, "pnorm")
    ```

    **Answer:** YOUR ANSWER.

    ***
    
2. (*35 pt*, Textbook Exercises 3.10) This question should be answered using the `Carseats` data set.

```{r}
head(Carseats)
```

(a) Fit a multiple regression model to predict `Sales` using `Price`, `Urban`, and `US`.

**Answer:** YOUR ANSWER.

```{r}
mod2 <- lm(Sales ~ Price+Urban+US,data=Carseats)
summary(mod2)
```

***

(b) Provide an interpretation of each coefficient in the model. Be careful—some of the variables in the model are qualitative!

**Answer:** YOUR ANSWER.

***

(c) Write out the model in equation form, being careful to handle the qualitative variables properly.

**Answer:** YOUR ANSWER.

***

(d) For which of the predictors can you reject the null hypothesis $H_0 : \beta_j = 0$?

**Answer:** YOUR ANSWER.

***

(e) On the basis of your response to the previous question, fit a smaller model that only uses the predictors for which there is evidence of association with the outcome.

**Answer:** YOUR ANSWER.
```{r}
mod2.2 = lm(formula=Sales~Price+US,data=Carseats)
summary(mod2.2)
```
***

(f) How well do the models in (a) and (e) fit the data?

**Answer:** YOUR ANSWER.

***

(g) Using the model from (e), obtain 95% confidence intervals for the coefficient(s).

**Answer:** YOUR ANSWER.

***

(h) Using the leave-one-out cross-validation and 5-fold cross-validation techniques to compare the performance of models in (a) and (e). What can you tell from (f) and (h)?

**Hint.** Functions `update` (with option `subset`) and `predict`.

**Answer:** YOUR ANSWER.
```{r}
## LOOCV
n = nrow(Carseats);
err_2.min = Inf;
err_2.2.min = Inf;
mod2.min = mod2;
mod2.2.min = mod2.2;
for(i in 1:n)
{
  update(mod2,data=Carseats[-i,]);
  err_2 = (predict(mod2,Carseats[i,])-Carseats[i,1])^2;
  if (err_2 < err_2.min)
  {
    err_2.min = err_2;
    mod2.min = mod2;
  }
  update(mod2.2,data=Carseats[-i,]);
  err_2.2 = (predict(mod2.2,Carseats[i,])-Carseats[i,1])^2;
  if (err_2.2 < err_2.2.min)
  {
    err_2.2.min = err_2.2;
    mod2.2.min = mod2.2;
  }
}
mse_2 = mean((Carseats[,1]-predict(mod2.min))^2);
mse_2.2 = mean((Carseats[,1]-predict(mod2.2.min))^2);
print(mse_2)
print(mse_2.2)
update(mod2,data=Carseats);
update(mod2.2,data=Carseats);
```
```{r}
## 5-FCV
n = nrow(Carseats);
err_2.min = Inf;
err_2.2.min = Inf;
mod2.min = mod2;
mod2.2.min = mod2.2;
for(i in seq(from=1,to=n-80,by=80))
{
  update(mod2,data=Carseats[-(i:i+80),]);
  err_2 = mean((predict(mod2,Carseats[i:i+80,])-Carseats[i:i+80,1])^2);
  if (err_2 < err_2.min)
  {
    err_2.min = err_2;
    mod2.min = mod2;
  }
  update(mod2.2,data=Carseats[-(i:i+80),]);
  err_2.2 = (predict(mod2.2,Carseats[i:i+80,])-Carseats[i:i+80,1])^2;
  if (err_2.2 < err_2.2.min)
  {
    err_2.2.min = err_2.2;
    mod2.2.min = mod2.2;
  }
}
mse_2 = mean((Carseats[,1]-predict(mod2.min))^2);
mse_2.2 = mean((Carseats[,1]-predict(mod2.2.min))^2);
print(mse_2)
print(mse_2.2)
update(mod2,data=Carseats);
update(mod2.2,data=Carseats);
```
***
```{r}
X <- rnorm(100)
epsilon <- rnorm(100)
beta <- c(2,2,-3,0.3)
Y <- beta[1]+beta[2]*X+beta[3]*X^2+beta[4]*X^3+epsilon
print(Y)
```
